The human in the loop: volunteer-based metacomputers as a socio-technical system

### 2016-04-23 Alife16/paper.tex
Fixing Issue #115
Issue #115 @JJ please read it to see if it is more clear

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer 
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many other researchers have
%Pablo: Desell in 2008 is not so recent
used Java \citep{chong:1999:jDGPi} and others have gone away from the
server-based paradigm to embrace peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These computing
platforms avoid single points of failure (the server) but, since they
need a certain amount of infrastructure installed to start, the
threshold to join them is much lower; this makes gathering new users
immediate and spontaneous, so that they can be used for short
algorithms on call.

>>>>

JavaScript can be used for either unwitting
\citep{unwitting-ec,boldrin2007distributed} or volunteer 
\citep{langdon:2005:metas,gecco07:workshop:dcor} distributed
evolutionary computation and it has been used ever since by several
authors, including more recent efforts
\citep{Desell:2008:AHG:1389095.1389273,duda2013distributed,DBLP:journals/corr/abs-0801-1210}. Many other researchers have
%Pablo: Desell in 2008 is not so recent
used Java \citep{chong:1999:jDGPi} and others have gone away from the
server-based paradigm to embrace peer to peer systems
\citep{jin2006constructing,10.1109/ICICSE.2008.99,DBLP:conf/3pgcic/GuervosMFEL12}. These computing
platforms to avoid single points of failure (the server) but, since they
need a certain amount of infrastructure installed in the client, the
threshold to join them is much lower; but once the infrastructure of P2P systems is in place
the gathering of new users becomes 
immediate and spontaneous, so that they can be used for short
algorithms on call.
